Taking Linear Logic Apart

### 2018-04-20 doc/tlla2018/main.tex
Finished proofs for TLLA

\documentclass[submission,copyright,creativecommons]{eptcs}
\providecommand{\event}{Linearity and TLLA 2018}
\usepackage{breakurl} % Not needed if you use pdflatex only.
\usepackage{underscore} % Only needed if you use pdflatex.
\usepackage{textcomp,textgreek,upgreek}
\usepackage{amsthm}
\newtheorem{definition}{Definition}
\newtheorem{lemma}{Lemma}
\newtheorem{theorem}{Theorem}
\newtheorem{corollary}{Corollary}
\input{preamble-typing}

@@

%% Classical Processes

@@

%% Hypersequent Classical Processes

\begin{definition}[Terms]\label{def:hcp-terms}
  \begin{gather*}
    \begin{array}{rllrll}
      \tm{P}, \tm{Q}, \tm{R}
           :=& \tm{\cpLink{x}{y}}         &\text{link}
      &  \mid& \tm{\piHalt}               &\text{terminated process}
      \\ \mid& \tm{\piNew{x}{P}}          &\text{name restriction, ``new''}
      &  \mid& \tm{( \piPar{P}{Q} )}      &\text{parallel composition, ``mix''}
      \\ \mid& \tm{\piBoundSend{x}{y}{P}} &\text{output}
      &  \mid& \tm{\piRecv{x}{y}{P}}      &\text{input}
      \\ \mid& \tm{\piBoundSend{x}{}{P}}  &\text{``halt''}
      &  \mid& \tm{\cpWait{x}{}{P}}       &\text{wait}
      \\ \mid& \tm{\cpInl{x}{P}}          &\text{select left choice}
      &  \mid& \tm{\cpInr{x}{P}}          &\text{select right choice}
      \\ \mid& \tm{\cpCase{x}{P}{Q}}      &\text{offer binary choice}
      &  \mid& \tm{\cpAbsurd{x}}          &\text{offer nullary choice}
    \end{array}
  \end{gather*}
\end{definition}

@@

\begin{definition}[Reduction]\label{def:hcp-reduction}
  A reduction $\reducesto{P}{Q}$ denotes that the process $\tm{P}$ can reduce
  to the process $\tm{Q}$ in a single step. Reductions can only be constructed
  as follows:
  \begin{gather*}
    \begin{array}{llcll}
      &
      & \vdots
      &
      \\
      \cpRedBetaTensParr
      & \tm{\cpCut{x}{\piSend{x}{y}{P}}{\piRecv{x}{z}{R}}}
      & \Longrightarrow
      & \tm{\piNew{x}{\piNew{y}{(\piPar{P}{\cpSub{y}{z}{R}})}}}
      \\
      \cpRedBetaOneBot
      & \tm{\cpCut{x}{\piSend{x}{}{P}}{\piRecv{x}{}{P}}}
      & \Longrightarrow
      & \tm{\piPar{P}{Q}}
      \\
      &
      & \vdots
      &
    \end{array}
  \end{gather*}
  \begin{center}
    \begin{prooftree*}
      \AXC{$\reducesto{P}{P^\prime}$}
      \SYM{\hccpRedGammaNew}
      \UIC{$\reducesto{\piNew{x}{P}}{\piNew{x}{P^\prime}}$}
    \end{prooftree*}
    \begin{prooftree*}
      \AXC{$\reducesto{P}{P^\prime}$}
      \SYM{\hccpRedGammaMix}
      \UIC{$\reducesto{\piPar{P}{Q}}{\piPar{P^\prime}{Q}}$}
    \end{prooftree*}
    \begin{prooftree*}
      \AXC{$\tm{P}\equiv\tm{Q}$}
      \AXC{$\reducesto{Q}{Q^\prime}$}
      \AXC{$\tm{Q^\prime}\equiv\tm{P^\prime}$}
      \SYM{\hccpRedGammaEquiv}
      \TIC{$\reducesto{P}{P^\prime}$}
    \end{prooftree*}
  \end{center}
  The relations $\Longrightarrow^{?}$, $\Longrightarrow^{+}$, and
  $\Longrightarrow^\star$ are the reflexive, transitive and reflexive,
  transitive closures of $\Longrightarrow$. 
\end{definition}

@@

\begin{theorem}\label{thm:cp2hcp-typing}
  If $\seq[P]{\Gamma}$ in \cp, then $\seq[\mtf{P}]{\Gamma}$ in \hcp.
\end{theorem}
\begin{proof}
  By induction on the structure of the derivation of $\seq[P]{\Gamma}$.
    \begin{itemize}
  \item 
    Case \textsc{Cut}.
    We rewrite as follows:
    \begin{center}
      \scalebox{0.9}{\(
        \begin{array}{lcl}
          \AXC{$\seq[P]{\mathcal{G} \hsep \tmty{x}{A}, \Gamma}$}
          \AXC{$\seq[Q]{\mathcal{H} \hsep \tmty{x}{A^\bot}, \Delta}$}
          \NOM{Cut}
          \BIC{$\seq[\cpCut{x}{P}{Q}]{
          \mathcal{G} \hsep \mathcal{H} \hsep \Gamma, \Delta}$}
          \DisplayProof
          & \Rightarrow
          & \AXC{$\seq[\mtf{P}]{\mathcal{G} \hsep \tmty{x}{A}, \Gamma}$}
            \AXC{$\seq[\mtf{Q}]{\mathcal{H} \hsep \tmty{x}{A^\bot}, \Delta}$}
            \NOM{H-Mix} 
            \BIC{$\seq[\piPar{\mtf{P}}{\mtf{Q}}]{
            \mathcal{G} \hsep \mathcal{H} \hsep
            \tmty{x}{A}, \Gamma \hsep \tmty{x}{A^\bot}, \Delta}$}
            \NOM{H-Cycle}
            \UIC{$\seq[\piNew{x}{(\piPar{\mtf{P}}{\mtf{Q}})}]{
            \mathcal{G} \hsep \mathcal{H} \hsep \Gamma, \Delta}$}
            \DisplayProof
        \end{array}
        \)}
    \end{center}
  \item
    Case $(\tens)$.
    We rewrite as follows:
    \begin{center}
      \scalebox{0.9}{\(
        \begin{array}{lcl}
          \AXC{$\seq[P]{\mathcal{G} \hsep \tmty{y}{A}, \Gamma}$}
          \AXC{$\seq[Q]{\mathcal{H} \hsep \tmty{x}{B}, \Delta}$}
          \SYM{\tens}
          \BIC{$\seq[\cpSend{x}{y}{P}{Q}]{
          \mathcal{G} \hsep \mathcal{H} \hsep \tmty{x}{A \tens B}, \Gamma, \Delta}$}
          \DisplayProof
          & \Rightarrow
          & \AXC{$\seq[\mtf{P}]{\mathcal{G} \hsep \tmty{y}{A}, \Gamma}$}
            \AXC{$\seq[\mtf{Q}]{\mathcal{H} \hsep \tmty{x}{B}, \Delta}$}
            \NOM{H-Mix}
            \BIC{$\seq[\piPar{\mtf{P}}{\mtf{Q}}]{
            \mathcal{G} \hsep \mathcal{H} \hsep
            \tmty{y}{A}, \Gamma \hsep \tmty{x}{B}, \Delta}$}
            \NOM{H-Cycle}
            \UIC{$\seq[\piNew{x}{(\piPar{\mtf{P}}{\mtf{Q}})}]{
            \mathcal{G} \hsep \mathcal{H} \hsep \Gamma, \Delta}$}
            \DisplayProof
        \end{array}
        \)}
    \end{center}
  \item
    Case $(\one)$.
    We rewrite as follows:
    \begin{center}
      \scalebox{0.9}{\(
        \begin{array}{lcl}
          \AXC{}\SYM{\one}
          \UIC{$\seq[\cpHalt{x}]{\tmty{x}{\one}}$}
          \DisplayProof
          & \Rightarrow
          & \AXC{}
            \NOM{H-Halt}
            \UIC{$\seq[\piHalt]{\emptyhypercontext}$}
            \SYM{\one}
            \UIC{$\seq[\piBoundSend{x}{}{\piHalt}]{\tmty{x}{\one}}$}
            \DisplayProof
        \end{array}      
        \)}
    \end{center}
  \end{itemize}
  The other cases are trivial.
\end{proof}

\begin{definition}\label{def:hcp-bigparr}
  We can interpret environments as types by collapsing them using a series
  of pars.
  \begin{gather*}
    \begin{array}{lcl}
      \ty{\bigparr(\emptycontext)}
      & = & \ty{\bot}
      \\
      \ty{\bigparr(\tmty{x_1}{A_1} , \dots , \tmty{x_n}{A_n})}
      & = & \ty{A_1 \parr \dots \parr A_n}
    \end{array}
  \end{gather*}
\end{definition}

\begin{lemma}\label{lem:hcp-bigparr}
  If $\seq{\Gamma}$ in \hcp, then $\seq{\bigparr\Gamma}$ in \hcp.
\end{lemma}
\begin{proof}
  By induction on the structure of $\Gamma$.
  \begin{itemize}
  \item
    If $\ty{\Gamma} = \ty{A}$, then the statement is trivially true.
  \item
    If $\ty{\Gamma} = \ty{A, B, \Gamma'}$,
    then we apply $(\parr)$ to get $\seq{A \parr B, \Gamma'}$,\\
    and apply the induction hypothesis.
  \end{itemize}
\end{proof}

\begin{definition}\label{def:hcp-bigtens}
  We can interpret hyper-environments as types by collapsing them using a series
  of tensors. In the case of the empty hyper-environment
  $\ty{\emptyhypercontext}$, we interpret this as the unit of tensor.
  \begin{gather*}
    \begin{array}{lcl}
      \ty{\bigtens(\emptyhypercontext)}
      & = & \ty{\one}
      \\
      \ty{\bigtens(\Gamma_1 \hsep \dots \hsep \Gamma_n)}
      & = & \ty{\bigparr\Gamma_1 \tens \dots \tens \bigparr\Gamma_n}
    \end{array}
  \end{gather*}
\end{definition}

\begin{theorem}\label{thm:hcp2cp-bigtens}
  If $\seq{\mathcal{G}}$ in \hcp, then $\seq{\bigtens\mathcal{G}}$ in \cp.
\end{theorem}

>>>>

\documentclass[submission,copyright,creativecommons]{eptcs}
\providecommand{\event}{Linearity and TLLA 2018}
\usepackage{nameref,hyperref,cleveref}
\usepackage[inline]{enumitem}
\usepackage{breakurl} % Not needed if you use pdflatex only.
\usepackage{underscore} % Only needed if you use pdflatex.
\usepackage{textcomp,textgreek,upgreek}
\usepackage{amsthm}
\newtheorem{definition}{Definition}
\newtheorem{lemma}{Lemma}
\newtheorem{theorem}{Theorem}
\newtheorem{corollary}{Corollary}
\input{preamble-typing}

@@

\section{Classical Processes}

@@

\section{Hypersequent Classical Processes}

\begin{definition}[Terms]\label{def:hcp-terms}
  \begin{gather*}
    \begin{array}{rllrll}
      \tm{P}, \tm{Q}, \tm{R}
           :=& \tm{\cpLink{x}{y}}         &\text{link}
      &  \mid& \tm{\piHalt}               &\text{terminated process}
      \\ \mid& \tm{\piNew{x}{P}}          &\text{name restriction, ``new''}
      &  \mid& \tm{( \piPar{P}{Q} )}      &\text{parallel composition, ``mix''}
      \\ \mid& \tm{\piBoundSend{x}{y}{P}} &\text{``output''}
      &  \mid& \tm{\piRecv{x}{y}{P}}      &\text{``input''}
      \\ \mid& \tm{\piBoundSend{x}{}{P}}  &\text{``halt''}
      &  \mid& \tm{\cpWait{x}{}{P}}       &\text{wait}
      \\ \mid& \tm{\cpInl{x}{P}}          &\text{select left choice}
      &  \mid& \tm{\cpInr{x}{P}}          &\text{select right choice}
      \\ \mid& \tm{\cpCase{x}{P}{Q}}      &\text{offer binary choice}
      &  \mid& \tm{\cpAbsurd{x}}          &\text{offer nullary choice}
    \end{array}
  \end{gather*}
\end{definition}

@@

\begin{definition}[Reduction]\label{def:hcp-reduction}
  A reduction $\reducesto{P}{Q}$ denotes that the process $\tm{P}$ can reduce
  to the process $\tm{Q}$ in a single step.
  The relation $\Longrightarrow^\star$ is the reflexive, transitive closure of
  $\Longrightarrow$.
  Reductions can be constructed as using the rules from \cref{def:cp-reduction},
  with the following changes:
  \begin{gather*}
    \begin{array}{llcll}
      &
      & \vdots
      &
      \\
      \cpRedBetaTensParr
      & \tm{\cpCut{x}{\piSend{x}{y}{P}}{\piRecv{x}{z}{R}}}
      & \Longrightarrow
      & \tm{\piNew{x}{\piNew{y}{(\piPar{P}{\cpSub{y}{z}{R}})}}}
      \\
      \cpRedBetaOneBot
      & \tm{\cpCut{x}{\piSend{x}{}{P}}{\piRecv{x}{}{P}}}
      & \Longrightarrow
      & \tm{\piPar{P}{Q}}
      \\
      &
      & \vdots
      &
    \end{array}
  \end{gather*}
  \begin{center}
    \begin{prooftree*}
      \AXC{$\reducesto{P}{P^\prime}$}
      \SYM{\hccpRedGammaNew}
      \UIC{$\reducesto{\piNew{x}{P}}{\piNew{x}{P^\prime}}$}
    \end{prooftree*}
    \begin{prooftree*}
      \AXC{$\reducesto{P}{P^\prime}$}
      \SYM{\hccpRedGammaMix}
      \UIC{$\reducesto{\piPar{P}{Q}}{\piPar{P^\prime}{Q}}$}
    \end{prooftree*}
    \begin{prooftree*}
      \AXC{$\tm{P}\equiv\tm{Q}$}
      \AXC{$\reducesto{Q}{Q^\prime}$}
      \AXC{$\tm{Q^\prime}\equiv\tm{P^\prime}$}
      \SYM{\hccpRedGammaEquiv}
      \TIC{$\reducesto{P}{P^\prime}$}
    \end{prooftree*}
  \end{center}
\end{definition}

@@

\section{Relation between \cp and \hcp}

\begin{definition}\label{def:cp2hcp-terms}
  We define a translation from terms in \cp to terms in \hcp which breaks down
  the term constructs in \cp into their more atomic constructs in \hcp.
  \[
    \begin{array}{lcllcl}
         \tm{\mtf{\cpLink{x}{y}}}
      &  := & \tm{\cpLink{x}{y}}
      &  \tm{\mtf{\cpCut{x}{P}{Q}}}
      &  := & \tm{\piNew{x}{(\piPar{\mtf{P}}{\mtf{Q}})}}
      \\ \tm{\mtf{\cpSend{x}{y}{P}{Q}}}
      &  := & \tm{\piBoundSend{x}{y}{(\piPar{\mtf{P}}{\mtf{Q}})}}
      &  \tm{\mtf{\cpRecv{x}{y}{P}}}
      &  := & \tm{\piRecv{x}{y}{\mtf{P}}}
      \\ \tm{\mtf{\cpHalt{x}}}
      &  := & \tm{\piBoundSend{x}{}{\piHalt}}
      &  \tm{\mtf{\cpWait{x}{P}}}
      &  := & \tm{\piRecv{x}{}{\mtf{P}}}
      \\ \tm{\mtf{\cpInl{x}{P}}}
      &  := & \tm{\cpInl{x}{\mtf{P}}}
      &  \tm{\mtf{\cpInr{x}{P}}}
      &  := & \tm{\cpInr{x}{\mtf{P}}}
      \\ \tm{\mtf{\cpCase{x}{P}{Q}}}
      &  := & \tm{\cpCase{x}{\mtf{P}}{\mtf{Q}}}
      &  \tm{\mtf{\cpAbsurd{x}}}
      &  := & \tm{\cpAbsurd{x}}
    \end{array}
  \]
\end{definition}

\begin{theorem}\label{thm:cp2hcp-typing}
  If $\seq[P]{\Gamma}$ in \cp, then $\seq[\mtf{P}]{\Gamma}$ in \hcp.
\end{theorem}
\begin{proof}
  By induction on the structure of the derivation of $\seq[P]{\Gamma}$.
    \begin{itemize}
  \item 
    Case \textsc{Cut}.
    We rewrite to:
    \[
      \begin{array}{lcl}
        \AXC{$\seq[P]{\Gamma, \tmty{x}{A}}$}
        \AXC{$\seq[Q]{\Delta, \tmty{x}{A^\bot}}$}
        \NOM{Cut}
        \BIC{$\seq[\cpCut{x}{P}{Q}]{\Gamma, \Delta}$}
        \DisplayProof
        & \Rightarrow
        & \AXC{$\seq[\mtf{P}]{\Gamma, \tmty{x}{A}}$}
          \AXC{$\seq[\mtf{Q}]{\Delta, \tmty{x}{A^\bot}}$}
          \NOM{H-Mix} 
          \BIC{$\seq[\piPar{\mtf{P}}{\mtf{Q}}]{
          \Gamma, \tmty{x}{A} \hsep \Delta, \tmty{x}{A^\bot}}$}
          \NOM{H-Cycle}
          \UIC{$\seq[\piNew{x}{(\piPar{\mtf{P}}{\mtf{Q}})}]{
          \Gamma, \Delta}$}
          \DisplayProof
      \end{array}
    \]
  \item
    Case $(\tens)$.
    We rewrite as follows:
    \[
      \begin{array}{lcl}
        \AXC{$\seq[P]{\Gamma, \tmty{y}{A}}$}
        \AXC{$\seq[Q]{\Delta, \tmty{x}{B}}$}
        \SYM{\tens}
        \BIC{$\seq[\cpSend{x}{y}{P}{Q}]{\Gamma, \Delta, \tmty{x}{A \tens B}}$}
        \DisplayProof
        & \Rightarrow
        & \AXC{$\seq[\mtf{P}]{\Gamma, \tmty{y}{A}}$}
          \AXC{$\seq[\mtf{Q}]{\Delta, \tmty{x}{B}}$}
          \NOM{H-Mix}
          \BIC{$\seq[\piPar{\mtf{P}}{\mtf{Q}}]{
          \Gamma, \tmty{y}{A} \hsep \Delta, \tmty{x}{B}}$}
          \SYM{\tens}
          \UIC{$\seq[\piBoundSend{x}{y}{(\piPar{\mtf{P}}{\mtf{Q}})}]{
          \Gamma, \Delta, \tmty{x}{A \tens B}}$}
          \DisplayProof
      \end{array}
    \]
  \item
    Case $(\one)$.
    We rewrite as follows:
    \[
      \begin{array}{lcl}
        \AXC{}\SYM{\one}
        \UIC{$\seq[\cpHalt{x}]{\tmty{x}{\one}}$}
        \DisplayProof
        & \Rightarrow
        & \AXC{}
          \NOM{H-Halt}
          \UIC{$\seq[\piHalt]{\emptyhypercontext}$}
          \SYM{\one}
          \UIC{$\seq[\piBoundSend{x}{}{\piHalt}]{\tmty{x}{\one}}$}
          \DisplayProof
      \end{array}      
    \]
  \end{itemize}
  The other cases are trivial.
\end{proof}

\begin{theorem}\label{thm:cp2hcp-equiv}
  If $\tm{P}\equiv\tm{Q}$ in \cp, then $\tm{\mtf{P}}\equiv\tm{\mtf{Q}}$ in \hcp.
\end{theorem}
\begin{proof}
  By induction on the structure of the derivation of $\tm{P}\equiv\tm{Q}$.
  \begin{itemize}
  \item
    Case \cpEquivCutComm.
    \[
      \begin{array}{lcl}
        \tm{\piNew{x}{(\piPar{\mtf{P}}{\mtf{Q}})}}
        & \equiv & \text{by \hccpEquivMixComm}
        \\
        \tm{\piNew{x}{(\piPar{\mtf{Q}}{\mtf{P}})}}
      \end{array}
    \]
  \item
    Case \cpEquivCutAss1.
    \[
      \begin{array}{lcl}
        \tm{\piNew{x}{(\piPar{\mtf{P}}{\piNew{y}{(\piPar{\mtf{Q}}{\mtf{R}})}})}}
        & \equiv & \text{by \hccpEquivScopeExt2}
        \\
        \tm{\piNew{x}{\piNew{y}{(\piPar{\mtf{P}}{(\piPar{\mtf{Q}}{\mtf{R}})})}}}
        & \equiv & \text{by \hccpEquivNewComm}
        \\
        \tm{\piNew{y}{\piNew{x}{(\piPar{\mtf{P}}{(\piPar{\mtf{Q}}{\mtf{R}})})}}}
        & \equiv & \text{by \hccpEquivMixAss1}
        \\
        \tm{\piNew{y}{\piNew{x}{(\piPar{(\piPar{\mtf{P}}{\mtf{Q}})}{\mtf{R}})}}}
        & \equiv & \text{by \hccpEquivScopeExt1 and \hccpEquivMixComm}
        \\
        \tm{\piNew{y}{(\piPar{\piNew{x}{(\piPar{\mtf{P}}{\mtf{Q}})}}{\mtf{R}})}}
      \end{array}
    \]
  \end{itemize}
  The other cases are trivial.
\end{proof}

\begin{theorem}\label{thm:cp2hcp-reduction}
  If $\reducesto{P}{Q}$ in \cp, then $\reducesto{\mtf{P}}{\mtf{Q}}$ in \hcp.
\end{theorem}
\begin{proof}
  By induction on the structure of the derivation of $\reducesto{P}{Q}$.
  \begin{itemize}
  \item
    Case \cpRedBetaTensParr.
    \begin{gather*}
      \begin{array}{lcl}
        \tm{\piNew{x}{(\piPar{\piBoundSend{x}{y}{(\piPar{P}{Q})}}{\piRecv{x}{z}{R}})}}
        & \Longrightarrow & \text{by \hccpRedBetaTensParr}
        \\
        \tm{\piNew{x}{\piNew{y}{(\piPar{(\piPar{P}{Q})}{\cpSub{y}{z}{R}})}}}
        & \equiv & \text{by \hccpEquivNewComm}
        \\
        \tm{\piNew{y}{\piNew{x}{(\piPar{(\piPar{P}{Q})}{\cpSub{y}{z}{R}})}}}
        & \equiv & \text{by \hccpEquivMixAss1}
        \\
        \tm{\piNew{y}{\piNew{x}{(\piPar{P}{(\piPar{Q}{\cpSub{y}{z}{R}})})}}}
        & \equiv & \text{by \hccpEquivScopeExt1}
        \\
        \tm{\piNew{y}{(\piPar{P}{\piNew{x}{(\piPar{Q}{\cpSub{y}{z}{R}})}})}}
      \end{array}
    \end{gather*}
  \item
    Case \cpRedBetaOneBot.
    \begin{gather*}
      \begin{array}{lcl}
        \tm{\piNew{x}{(\piPar{\piBoundSend{x}{}{\piHalt}}{\piRecv{x}{}{\mtf{Q}}})}}
        & \Longrightarrow & \text{by \hccpRedBetaOneBot}
        \\
        \tm{(\piPar{\piHalt}{\mtf{Q}})}
        & \equiv & \text{by \hccpEquivMixHalt1}
        \\
        \tm{\mtf{Q}}
      \end{array}
    \end{gather*}
  \end{itemize}
  The other cases are trivial.
\end{proof}

\begin{definition}\label{def:bigparr}
  We can interpret environments as types by collapsing them using a series
  of pars.
  \begin{gather*}
    \begin{array}{lcl}
      \ty{\bigparr(\tmty{x_1}{A_1} , \dots , \tmty{x_n}{A_n})}
      & = & \ty{A_1 \parr \dots \parr A_n}
    \end{array}
  \end{gather*}
\end{definition}

\begin{lemma}\label{lem:cp-bigparr}
  If $\seq{\Gamma}$ in \cp, then $\seq{\bigparr\Gamma}$ in \cp.
\end{lemma}
\begin{proof}
  By induction on the structure of $\Gamma$.
  \begin{itemize}
  \item
    If $\ty{\Gamma} = \ty{A}$, then the statement is trivially true.
  \item
    If $\ty{\Gamma} = \ty{A, B, \Gamma'}$,
    then we apply $(\parr)$ to get $\seq{A \parr B, \Gamma'}$,\\
    and apply the induction hypothesis.
  \end{itemize}
\end{proof}

\begin{definition}\label{def:bigtens}
  We can interpret hyper-environments as types by collapsing them using a series
  of tensors. In the case of the empty hyper-environment
  $\ty{\emptyhypercontext}$, we interpret this as the unit of tensor.
  \begin{gather*}
    \begin{array}{lcl}
      \ty{\bigtens(\emptyhypercontext)}
      & = & \ty{\one}
      \\
      \ty{\bigtens(\Gamma_1 \hsep \dots \hsep \Gamma_n)}
      & = & \ty{\bigparr\Gamma_1 \tens \dots \tens \bigparr\Gamma_n}
    \end{array}
  \end{gather*}
\end{definition}

\begin{lemma}\label{lem:hcp2cp-split}
  If $\seq{\Gamma_1 \hsep \dots \hsep \Gamma_n}$ in \hcp,
  then there exist $\seq{\Gamma_1}, \dots, \seq{\Gamma_n}$ in \cp.
\end{lemma}
\begin{proof}  
  By induction on the structure of the derivation of
  $\seq{\Gamma_1 \hsep \dots \hsep \Gamma_n}$,
  taking care to remember the continuation of the derivation.
  \begin{itemize}
  \item 
    Case \textsc{Cycle}. We know there \emph{must} be a corresponding
    \textsc{H-Mix} deeper in the derivation. We have:
    \[
      \AXC{}\noLine\UIC{$\seq{\mathcal{G}_1}$}
      \AXC{}\noLine\UIC{$\seq{\mathcal{G}_2}$}
      \NOM{H-Mix}
      \BIC{$\seq{\mathcal{G}_1 \hsep \mathcal{G}_2}$}
      \DisplayProof
      \; \cdots f \cdots \;
      \AXC{}\noLine
      \UIC{$\seq{\mathcal{G}_3 \hsep \Gamma, A \hsep \Delta, A^\bot}$}
      \NOM{H-Cycle}
      \UIC{$\seq{\mathcal{G}_3 \hsep \Gamma, \Delta}$}
      \DisplayProof
      \; \cdots h \cdots \;
      \AXC{}\noLine
      \UIC{$\seq{\Gamma_1 \hsep \dots \hsep \Gamma_n}$}
      \DisplayProof
    \]
    By induction, we obtain some number of proofs in \cp corresponding
    to the sequents in $\ty{\mathcal{G}_1}$ and $\ty{\mathcal{G}_2}$.
    Each rule in $f$ modifies only one of these proofs (or joins two).
    Therefore we can split $f$, applying each rule to its corresponding proof
    (joining proofs as necessary).
    We now have several proofs, including two of $\seq{\Gamma, A}$ and
    $\seq{\Delta, A^\bot}$, which we join using \textsc{Cut}.
    Then we do the same for the rules in $h$.
  \item
    Case $(\tens)$. We know there \emph{must} be a corresponding
    \textsc{H-Mix} deeper in the derivation. We have:
    \[
      \AXC{}\noLine\UIC{$\seq{\mathcal{G}_1}$}
      \AXC{}\noLine\UIC{$\seq{\mathcal{G}_2}$}
      \NOM{H-Mix}
      \BIC{$\seq{\mathcal{G}_1 \hsep \mathcal{G}_2}$}
      \DisplayProof
      \; \cdots f \cdots \;
      \AXC{}\noLine\UIC{$\seq{\mathcal{G}_3 \hsep \Gamma, A \hsep \Delta, B}$}
      \SYM{\tens}
      \UIC{$\seq{\mathcal{G}_3 \hsep \Gamma, \Delta, {A \tens B}}$}
      \DisplayProof
      \; \cdots h \cdots \;
      \AXC{}\noLine\UIC{$\seq{\Gamma_1 \hsep \dots \hsep \Gamma_n}$}
      \DisplayProof
    \]
    By induction, we obtain some number of proofs in \cp corresponding
    to the sequents in $\ty{\mathcal{G}_1}$ and $\ty{\mathcal{G}_2}$.
    Each rule in $f$ modifies only one of these proofs (or joins two).
    Therefore we can split $f$, applying each rule to its corresponding proof
    (joining proofs as necessary).
    We now have several proofs, including two of $\seq{\Gamma, A}$ and
    $\seq{\Delta, B}$, which we join using $(\tens)$.
    Then we do the same for the rules in $h$.
  \item
    Case $(\one)$. We know there \emph{must} be a corresponding \textsc{H-Halt}
    deeper in the derivation. There are two cases: either the corresponding
    \textsc{H-Halt} follows immediately, in which case we rewrite the both rules
    to an application of $(\one)$ in \cp, or it is deeper in the proof, in which
    case it must be followed by an application of \textsc{Mix}. We have:
    \[
      \AXC{}
      \NOM{H-Halt}
      \UIC{\seq{\emptyhypercontext}}
      \AXC{}\noLine\UIC{$\seq{\mathcal{G}_1}$}
      \NOM{H-Mix}
      \BIC{$\seq{\mathcal{G}_1}$}
      \DisplayProof
      \; \cdots f \cdots \;
      \AXC{}\noLine\UIC{$\seq{\mathcal{G}_2}$} 
      \SYM{\one}
      \UIC{$\seq{\mathcal{G}_2 \hsep \one}$}
      \DisplayProof
      \; \cdots h \cdots \;
      \AXC{}\noLine
      \UIC{$\seq{\Gamma_1 \hsep \dots \hsep \Gamma_n}$}
      \DisplayProof
    \]
    By induction, we obtain some number of proofs in \cp corresponding
    to the sequents in $\ty{\mathcal{G}_1}$.
    Each rule in $f$ modifies only one of these proofs (or joins two).
    Therefore we can split $f$, applying each rule to its corresponding proof
    (joining proofs as necessary).
    We now have several proofs corresponding to the sequents in
    $\ty{\mathcal{G}_2}$.
    Then we do the same for the rules in $h$.
  \item
    Case \textsc{Mix}. We know that there is no application of \textsc{H-Cycle}
    or $(\tens)$ which eliminates the hypersequent separator introduced by this
    application of \textsc{Mix}. We have:
    \[
      \AXC{}\noLine\UIC{$\seq{\mathcal{G}_1}$}
      \AXC{}\noLine\UIC{$\seq{\mathcal{G}_2}$}
      \NOM{H-Mix}
      \BIC{$\seq{\mathcal{G}_1 \hsep \mathcal{G}_2}$}
      \DisplayProof
      \; \cdots f \cdots \;
      \AXC{}\noLine
      \UIC{$\seq{\Gamma_1 \hsep \dots \hsep \Gamma_n}$}
      \DisplayProof
    \]
    By induction, we obtain some number of proofs in \cp corresponding
    to the sequents in $\ty{\mathcal{G}_1}$ and $\ty{\mathcal{G}_2}$.
    Each rule in $f$ modifies only one of these proofs (or joins two).
    Therefore we can split $f$, applying each rule to its corresponding proof
    (joining proofs as necessary).
  \end{itemize}
\end{proof}

\begin{theorem}\label{thm:hcp2cp-bigtens}
  If $\seq{\mathcal{G}}$ in \hcp, then $\seq{\bigtens\mathcal{G}}$ in \cp.
\end{theorem}
\begin{proof}
  By case analysis on the structure of the hyper-environment $\ty{\mathcal{G}}$.
  \begin{itemize}
  \item
    If $\ty{\mathcal{G}} = \ty{\emptyhypercontext}$, we apply $(\one)$.
  \item
    If $\ty{\mathcal{G}} = \ty{\Gamma_1 \hsep \dots \hsep \Gamma_n}$,
    we apply \cref{lem:hcp2cp-split} to obtain proofs of $\seq{\Gamma_1}, \dots,
    \seq{\Gamma_n}$ in \cp, then we apply \cref{lem:cp-bigparr} to each of
    those proofs to obtain proofs of $\seq{\bigparr\Gamma_1}, \dots,
    \seq{\bigparr\Gamma_n}$, and join them using $(\tens)$ to obtain a single
    proof of $\seq{\bigtens\mathcal{G}}$ in \cp.
  \end{itemize}
\end{proof}
